Adopting agile in the large: motivations, success factors and challenges

### 2014-01-14 journal/article.tex
Text and example references on inclusion criteria

Examples on topics excluded by the first facet are agile manufacturing, and
applying Scrum practices in management boards, as these do not relate to
software engineering. In addition, we required that the organizational
transformation was aimed to introduce agile methods, which excluded other
development methods than agile (e.g. [Sagesser 2013]), and general talk on
organizational transformation.

The facet of \emph{organizational transformation} was interpreted so that the
primary study must present insights on the process of transformation. Some
topics that could clearly be excluded were discussing a large agile effort but

-- not presenting the how the organization had evolved [Fitzgerald?],
   Lyon [Lyon 2008] was excluded as it discusses technical challenges in scaling
   up an agile process instead of providing organizational viewpoints.

-- pilot cases that clearly span one limited project [Scott 2008?, Mc Cormic 2005],

-- a single team in a large organization [Fulgham, Jensen].

-- Some case studies that provide minimal information on the transformation process [Greening?].
   [Mishra 2011] discusses agile practices in a large organization, but does not
   provide viewpoints on the transformation process and introduction of agile methods.
   Kim [Kim 2012] sounds promising at a start, but merely presents agile tools
   lacking any transformation description.
   Also [Hodgkins].

Transformation and ``scaling up'' are very closely related and in some cases
they are one and the same. For instance, if transformation begins with a pilot
and spreads gradually through the organization, the process can very well be
seen as a ``scaling up'' journey. However, we did not include discussions purely
on scaling up, especially if no organizational change was considered. [Maranzato
2012, Lyon 2008]

The facet of \emph{large scale} was interpreted as presented in section
\ref{sec:largescale}.
--> Case of one agile team in an enterprise: This is unrelated if the single
    team has no effect on the rest of the enterprise. There is no
    ``organizational transformation'' if there is just one team soloing.

--> The case of difficult decision regarding size [Cloke 2007, Miller 2012].
--> [Tudor 2006] Exclude, borderline. There is no evidence on size. Many teams
    are mentioned, but there is still no direct indication of large size.

--> ``The team'' referring to a large organization [Hodgkins]

In addition to the criteria listed above we excluded studies that were not
empirical. We excluded textbooks, studies presenting theories, and other studies
that did not include any case organization. We also excluded student experiments
as it is implausible to simulate the dynamics of a large organization in an
experiment.

-- snip --
Listing of not included topics. Discussion on these topics are considered not
providing insight to the research questions. Our goal is to address the research
questions, and specifically focus on analyzing the transformation process.
Not included topics:
--> Benefits of agile in general, problems with agile in general
--> Comparing agile and method X
--> Reporting on the current method, without consideration of how the method has
    been evolved (or transformed)
Tämän perusteella pitää siis kertoa itse prosessista: --> Kirjoita auki tämä
kriteeri paremmin.

@@

\bibliography{sources_background,sources_primary}

>>>>

Examples on topics excluded by the first facet are agile manufacturing, and
applying Scrum practices in management boards, as these do not relate to
software engineering. In addition, we required that the organizational
transformation was aimed to introduce agile methods, which excluded other
development methods than agile \cite{Sagesser2013}, and use of agile
methods in other contexts than software development \cite{Hodgkins2007}.

The facet of \emph{organizational transformation} was interpreted so that the
primary study must present insights on the process of transformation. This
was the most important facet, as the pivot of this research is to examine
how the transformations happen. Examples on excluded topics are comparing the
original and agile development methods \cite{Petersen2010}, discussing use of
agile in a large organization but not describing how the new methods were
introduced \cite{Mishra2011}, and merely presenting agile tools in large scale
use \cite{Kim2012}. These sources were excluded as they did not privide insights
on organizational transformation.
% Also [Fitzgerald 2005] on just presenting use of agile methods, no introducing

Transformation and ``scaling up'' are very closely related and in some cases
they are one and the same. For instance, if transformation begins with a pilot
and spreads gradually through the organization, the process can very well be
seen as a ``scaling up'' journey. However, we excluded cases where a initially
small organization was scaled up \cite{Maranzato2012}, and discussions with a
process centered viewpoint without describing organizational change
\cite{Lyon2008}.
% Also [Greening 2010] on process centered viewpoint without transformation

The facet of \emph{large scale} was interpreted as presented in section
\ref{sec:largescale}, having 50 development personel or 6 teams as as the limit
for large scale. In some cases the source presented very vague indicators on
size. For instance, we deemed the case presented by Cloke \cite{Cloke2007} to be
included as there was indications of large scale considerations, although the
size remained unclear. The case presented by Miller and Haddad \cite{Miller2012}
was deemed to be excluded as there was no indications whatsoever on size. A
borderline exclude was the case presented by Tudor \cite{Tudor2006} as there was
no indication of large size, althoug there were many development teams.
To complicate matters, some papers talked about ``the team'' in singular when
referring to the organization \cite{Hodgkins2007}, making it clearly nontrivial
to judge whether an organization was large based on the choice of words of the
author.

A further example on exclusion by the \emph{large scale} facet were cases with
large organizations but only a single team adopting agile \cite{Fulgham2011}.
We considered cases of single teams (although in large organizations) unrelated
to this research as our focus is on transformation of the entire organization.
Also piloting cases that resulted only in single teams using agile were excluded
\cite{Scott2008}.

% Also [Jensen 2003] with only a single team
% Possibly [Mc Cormic 2005] on single team piloting

In addition to the criteria listed above we excluded studies that were not
empirical. We excluded textbooks, studies merely presenting theories, and other
studies that did not include any case organization. We also excluded studies of
benefits or limitations of agile in general. Lastly, we excluded student
experiments as it is implausible to simulate the dynamics of a large
organization in an experiment.

@@

\bibliography{sources_background,sources_primary,sources_excluded}
